Convective heat transport in stratified atmospheres at low and high Mach number

### 2016-11-17 tex/nusselt_paper.tex
fixes a few things in results section for easier reading.

The efficiency of convection is quantified by the Nusselt number.  
Nu is well-defined in RB convection
as the total flux normalized by the steady-state conductive flux 
\cite{johnston&doering2009, otero&all2002}.
In stratified convection Nu is more difficult to define, but one of the earliest definitions used
was \cite{graham1975,hurlburt&all1984}
\begin{equation}
\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}}{F_{\text{ref}} - F_{\text{A}}},
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the 
z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ 
is the adiabatic conductive flux and
$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
for an ideal gas in hydrostatic equilibrium.
$F_{\text{ref}} \equiv \Delta T / L_z$, 
where $\Delta T \equiv T(L_z) - T(0)$, is the 
conductive flux of a linear profile connecting the upper
and lower plates, which is constant for 
the choice of fixed-temperature boundaries.

@@

High Ma flows exhibit two 
local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a)
at large enough values of Ra for shocks to form.
Shock-heated fluid parcels sometimes gain vorticity as
they sink into the lower atmosphere.
This creates deep, rapidly-rotating regions
of mixing which persist for many overturn times. These ``spinners'' appear to
influence the dynamics, but their contributions are unclear.

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
\caption{Variation of Nu as Ra increases at high and low $\epsilon$. 
At high $\epsilon$ (purple circles), 
a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra At $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
our observed Nu scalings collapse onto a similar line which is
indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
 by the square root of the variance of the time-averaged Nu profile with depth and 
 indicate whether or not a solution is well-converged.
\label{fig:nu_v_ra} }
\end{figure}

>>>>

The efficiency of convection is quantified by the Nusselt number.  
Nu is well-defined in RB convection
as the total flux normalized by the steady-state conductive flux 
\cite{johnston&doering2009, otero&all2002}.
In stratified convection Nu is more difficult to define, but one of the earliest definitions used
was \cite{graham1975,hurlburt&all1984}
\begin{equation}
\text{Nu} \equiv \frac{F_{\text{conv, z}} + F_{\text{cond, z}} - F_{\text{A}}}{F_{\text{ref}} - F_{\text{A}}},
\label{eqn:nusselt}
\end{equation}
where $F_{\text{conv, z}}$ and $F_{\text{cond, z}}$ are the 
z-components of $\bm{F}_{\text{conv}}$ and $\bm{F}_{\text{cond}}$,
respectively.  $F_{\text{A}} \equiv -\kappa \partial_z T_{\text{ad}}$ 
is the adiabatic conductive flux and
$\partial_z T_{\text{ad}} \equiv - g / c_{P}$ 
for an ideal gas in hydrostatic equilibrium.
The conductive flux of a linear profile connecting the upper
and lower plates
is $F_{\text{ref}} \equiv \Delta T / L_z$, 
where $\Delta T \equiv T(L_z) - T(0)$.  $F_{\text{ref}}$ is constant for 
the choice of fixed-temperature boundaries.

@@

At large enough values of Ra for shocks to form,
high Ma flows exhibit two 
local maxima in the enthalpy flux and kinetic energy flux (Fig. \ref{fig:flux_profiles}a).
Shock-heated fluid parcels sometimes gain vorticity as
they sink into the lower atmosphere.
This creates deep, rapidly-rotating regions
of mixing which persist for many overturn times. These ``spinners'' appear to
influence the dynamics, but their contributions are unclear.

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
\caption{Variation of Nu as Ra increases at high and low $\epsilon$. 
At high $\epsilon$ (purple circles), 
a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra at $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
our observed Nu scalings collapse onto a similar line which is
indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
 by the square root of the variance of the time-averaged Nu profile with depth and 
 indicate whether or not a solution is well-converged.
\label{fig:nu_v_ra} }
\end{figure}
